An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-22 VLDB2026/main.tex
Update main.tex

		\item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground-truth $k$ nearest neighbors.
		\item \textbf{QPS (Queries Per Second)}: The number of queries processed per second.
		\item \textbf{Index Construction Time}: The total time required to transform the raw dataset into a queryable index structure.
		\item \textbf{Index Size}: The storage size of the persisted index on disk.
		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction.
	\end{enumerate}

@@

	We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1} and Table~\ref{tab:range_algo}. For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.

>>>>

		\item \textbf{Recall@k}: The proportion of overlap between the returned approximate $k$ nearest neighbors and the ground-truth $k$ nearest neighbors.
		\item \textbf{QPS (Queries Per Second)}: The number of queries processed per second.
		\item \textbf{Index Construction Time}: The total time required to transform the raw dataset into a queryable index structure.
		\item \textbf{Index Size}: The storage size of the persisted index on disk.
		\item \textbf{Peak Memory Usage}: The maximum memory consumption observed during index construction \textcolor{cyan}{and search}.
	\end{enumerate}

@@

	We summarize the multi-threading capabilities of each algorithm in Table~\ref{tab:compair_1}. For vector database systems, we adopt a multi-process evaluation scheme (rather than multi-threaded execution), following the methodology proposed in VectorDBBench~\cite{VectorDBBench}, to better reflect their real-world performance.
